---
title: "SBM-L Control Chart"
format:
  pdf:
    pdf-engine: xelatex
    keep-tex: true
    geometry:
      - left=2.5cm
      - right=2.5cm
      - top=2.5cm
      - bottom=2.5cm
  html:
    toc: true
    code-fold: false
    df-print: paged
number-sections: true
mainfont: "Times New Roman"
fontsize: 12pt
editor: visual
execute:
  echo: true
  warning: true
  message: true
  cache: true
  freeze: auto
---

# SBM-L Control Chart

## Stage3A_SBM_L Function


```{r setup}
library(readxl)
library(dplyr)
library(tidyr)
library(ggplot2)
library(purrr)

set.seed(123)
setwd("C:/Users/xyang1/CV Research Paper/stability paper")
file="C:/Users/xyang1/CV Research Paper/stability paper/Equipment_A.xlsx"
```


```{r}
stage3A_SBM_L <- function(file,
                          target_ARL0 = 740,
                          B = 10000,
                          c_smooth = 0.5,
                          seed = 123,
                          event_col = "Event",
                          location_col = "Location",
                          result_col = "Result",
                          lod_col = "LOD",
                          loq_col = "LOQ",
                          usl_col = "USL",
                          plot_chart = TRUE) {
  
  required_pkgs <- c("readxl", "dplyr", "tidyr", "ggplot2", "purrr")
  missing_pkgs <- required_pkgs[!(required_pkgs %in% installed.packages()[, "Package"])]
  
  if (length(missing_pkgs) > 0) {
    stop(
      "Please install the following packages first: ",
      paste(missing_pkgs, collapse = ", ")
    )
  }
  
  library(readxl)
  library(dplyr)
  library(tidyr)
  library(ggplot2)
  library(purrr)
  
  set.seed(seed)
  
  
  # ARL0-based calibration
  
  
  if (target_ARL0 <= 1) {
    stop("target_ARL0 must be greater than 1.")
  }
  
  alpha <- 1 / target_ARL0
  

  # Step 0: Identify available sheets
 
  
  all_sheets <- readxl::excel_sheets(file)
  residue_types <- c("DAR", "CAR", "Mic")
  available_types <- intersect(residue_types, all_sheets)
  
  if (length(available_types) == 0) {
    stop("No valid sheets found. Sheet names must include at least one of: DAR, CAR, Mic.")
  }
  
  if (length(available_types) == 1) {
    stop(
      "Only one residue-type sheet was found: ",
      available_types,
      ". Please use the univariate control chart method instead of the multivariate SBM-L chart."
    )
  }
  
  message("Available residue types used in SBM-L chart: ",
          paste(available_types, collapse = ", "))
  
  message("Target ARL0 = ", target_ARL0,
          "; alpha = ", signif(alpha, 5))
  

  # Helper function: detect ND symbol
 
  
  is_nd_result <- function(x) {
    x_chr <- trimws(toupper(as.character(x)))
    x_chr %in% c("ND", "NON-DETECT", "NONDETECT")
  }
  
  
  # Step 1 and Step 2:
  # Read each sheet, replace ND by LOD or LOQ, normalize by USL

  
  read_and_normalize <- function(type) {
    
    dat <- readxl::read_excel(file, sheet = type)
    
    # Choose actual result column.
    # Usually CAR and Mic use "Result".
    # DAR may use "DAR" as the result column.
    result_col_actual <- result_col
    
    if (!(result_col_actual %in% names(dat)) && type %in% names(dat)) {
      result_col_actual <- type
    }
    
    required_cols <- c(
      event_col, location_col, result_col_actual,
      lod_col, loq_col, usl_col
    )
    
    missing_cols <- setdiff(required_cols, names(dat))
    
    if (length(missing_cols) > 0) {
      stop(
        "Sheet ", type, " is missing required columns: ",
        paste(missing_cols, collapse = ", ")
      )
    }
    
    dat2 <- dat %>%
      mutate(
        ResidueType = type,
        Event = suppressWarnings(as.numeric(.data[[event_col]])),
        Location = as.character(.data[[location_col]]),
        
        Result_chr = trimws(as.character(.data[[result_col_actual]])),
        ND_flag = is_nd_result(Result_chr),
        
        Result_raw = suppressWarnings(as.numeric(Result_chr)),
        LOD = suppressWarnings(as.numeric(.data[[lod_col]])),
        LOQ = suppressWarnings(as.numeric(.data[[loq_col]])),
        USL = suppressWarnings(as.numeric(.data[[usl_col]])),
        
        Result_Replacement_Source = case_when(
          ND_flag & !is.na(LOD) ~ "ND replaced by LOD",
          ND_flag & is.na(LOD) & !is.na(LOQ) ~ "ND replaced by LOQ",
          ND_flag & is.na(LOD) & is.na(LOQ) ~ "Removed: ND with missing LOD and LOQ",
          !ND_flag & !is.na(Result_raw) ~ "Observed Result",
          !ND_flag & is.na(Result_raw) ~ "Removed: missing or nonnumeric Result",
          TRUE ~ NA_character_
        ),
        
        Result_ND_Replaced = case_when(
          ND_flag & !is.na(LOD) ~ LOD,
          ND_flag & is.na(LOD) & !is.na(LOQ) ~ LOQ,
          ND_flag & is.na(LOD) & is.na(LOQ) ~ NA_real_,
          !ND_flag & !is.na(Result_raw) ~ Result_raw,
          !ND_flag & is.na(Result_raw) ~ NA_real_,
          TRUE ~ NA_real_
        )
      )
    
    n_removed_nd_missing_lod_loq <- sum(
      dat2$ND_flag & is.na(dat2$LOD) & is.na(dat2$LOQ),
      na.rm = TRUE
    )
    
    n_removed_missing_result <- sum(
      !dat2$ND_flag & is.na(dat2$Result_raw),
      na.rm = TRUE
    )
    
    if (n_removed_nd_missing_lod_loq > 0) {
      warning(
        "Sheet ", type, ": ",
        n_removed_nd_missing_lod_loq,
        " ND row(s) were removed because both LOD and LOQ were missing."
      )
    }
    
    if (n_removed_missing_result > 0) {
      warning(
        "Sheet ", type, ": ",
        n_removed_missing_result,
        " row(s) were removed because Result was missing or nonnumeric."
      )
    }
    
    dat2 <- dat2 %>%
      filter(
        !(ND_flag & is.na(LOD) & is.na(LOQ)),
        !(!ND_flag & is.na(Result_raw))
      )
    
    if (any(is.na(dat2$USL))) {
      stop("Missing or nonnumeric USL detected in sheet ", type, ".")
    }
    
    if (any(dat2$USL <= 0, na.rm = TRUE)) {
      stop("USL must be positive in sheet ", type, ".")
    }
    
    dat2 <- dat2 %>%
      mutate(
        Normalized = 100 * Result_ND_Replaced / USL
      )
    
    if (any(is.na(dat2$Normalized))) {
      warning(
        "Missing normalized values detected in sheet ",
        type,
        ". Please check Result, LOD, LOQ, and USL."
      )
    }
    
    dat2 %>%
      select(
        ResidueType, Event, Location,
        Result_chr, Result_raw,
        LOD, LOQ, USL,
        ND_flag, Result_Replacement_Source,
        Result_ND_Replaced, Normalized
      )
  }
  
  normalized_data <- purrr::map_dfr(available_types, read_and_normalize)
  
 
  # Step 3: Event-level medians

  
  event_medians_long <- normalized_data %>%
    group_by(ResidueType, Event) %>%
    summarise(
      EventMedian = median(Normalized, na.rm = TRUE),
      .groups = "drop"
    )
  
  event_medians_wide <- event_medians_long %>%
    tidyr::pivot_wider(
      id_cols = Event,
      names_from = ResidueType,
      values_from = EventMedian
    ) %>%
    arrange(Event)
  
  partially_missing_events <- event_medians_wide %>%
    filter(
      if_any(all_of(available_types), ~ is.na(.x)) &
        if_any(all_of(available_types), ~ !is.na(.x))
    )
  
  if (nrow(partially_missing_events) > 0) {
    warning(
      "Some cleaning events have one or more missing residue-type medians. ",
      "These events will be retained, and the monitoring statistic will be ",
      "calculated using available residue-type values."
    )
  }
  
  events_all_missing <- event_medians_wide %>%
    filter(
      if_all(all_of(available_types), ~ is.na(.x))
    )
  
  if (nrow(events_all_missing) > 0) {
    warning(
      "Some cleaning events have all available residue-type medians missing. ",
      "These events will be removed from monitoring statistic calculation."
    )
  }
  
  event_medians_wide_complete <- event_medians_wide %>%
    filter(
      if_any(all_of(available_types), ~ !is.na(.x))
    )
  
  n_events <- nrow(event_medians_wide_complete)
  
  if (n_events < 3) {
    stop(
      "Too few cleaning events with at least one available residue-type median ",
      "for Stage 3A SBM-L calibration."
    )
  }
  
  
  # Step 4: Global robust centers

  
  global_centers <- event_medians_wide_complete %>%
    summarise(across(all_of(available_types), ~ median(.x, na.rm = TRUE)))
  
  theta0 <- as.numeric(global_centers[1, available_types])
  names(theta0) <- available_types
  
 
  # Step 5: Observed monitoring statistics

  
  observed_stats <- event_medians_wide_complete
  
  for (type in available_types) {
    center_value <- theta0[type]
    observed_stats[[paste0("Dplus_", type)]] <- pmax(
      0,
      observed_stats[[type]] - center_value
    )
  }
  
  dplus_cols <- paste0("Dplus_", available_types)
  
  observed_stats <- observed_stats %>%
    rowwise() %>%
    mutate(
      T_stat = max(c_across(all_of(dplus_cols)), na.rm = TRUE)
    ) %>%
    ungroup()
  

  # Step 6: Location-stratified smoothed bootstrap

  
  bootstrap_one_type <- function(type, dat_source = normalized_data) {
    
    dat_type <- dat_source %>%
      filter(ResidueType == type)
    
    locations <- sort(unique(dat_type$Location))
    boot_values <- numeric(length(locations))
    
    for (m in seq_along(locations)) {
      
      loc <- locations[m]
      
      g_loc <- dat_type %>%
        filter(Location == loc) %>%
        pull(Normalized)
      
      g_loc <- g_loc[!is.na(g_loc)]
      
      if (length(g_loc) == 0) {
        boot_values[m] <- NA_real_
        next
      }
      
      med_g <- median(g_loc)
      mad_g <- median(abs(g_loc - med_g))
      h_loc <- c_smooth * mad_g
      
      sampled_value <- sample(g_loc, size = 1, replace = TRUE)
      eps <- rnorm(1, mean = 0, sd = h_loc)
      
      boot_values[m] <- max(0, sampled_value + eps)
    }
    
    median(boot_values, na.rm = TRUE)
  }
  
  generate_one_T <- function(dat_source = normalized_data) {
    
    boot_medians <- sapply(
      available_types,
      function(type) bootstrap_one_type(type, dat_source = dat_source)
    )
    
    boot_dplus <- pmax(0, boot_medians - theta0[available_types])
    
    max(boot_dplus, na.rm = TRUE)
  }
  
  T_boot <- numeric(B)
  
  for (b in seq_len(B)) {
    T_boot[b] <- generate_one_T()
  }
  

  # Step 7: ARL0-based UCL

  
  UCL_L <- as.numeric(
    quantile(T_boot, probs = 1 - alpha, na.rm = TRUE, type = 7)
  )
  
  empirical_p0 <- mean(T_boot > UCL_L, na.rm = TRUE)
  empirical_ARL0 <- ifelse(empirical_p0 > 0, 1 / empirical_p0, Inf)
  

  # Step 8: Monitoring rule and chart

  
  chart_data <- observed_stats %>%
    mutate(
      UCL_L = UCL_L,
      Signal = T_stat > UCL_L
    )
  
  p <- ggplot(chart_data, aes(x = Event, y = T_stat, group = 1)) +
    geom_line(color = "black") +
    geom_point(aes(color = Signal), size = 2.5) +
    geom_hline(
      yintercept = UCL_L,
      linetype = "dashed",
      color = "red",
      linewidth = 0.8
    ) +
    scale_color_manual(values = c("FALSE" = "black", "TRUE" = "red")) +
    labs(
      title = "Stage 3A SBM-L Control Chart",
      subtitle = paste0(
        "Residue types: ", paste(available_types, collapse = ", "),
        "; target ARL0 = ", target_ARL0,
        "; alpha = ", signif(alpha, 4),
        "; UCL = ", signif(UCL_L, 4)
      ),
      x = "Cleaning Event",
      y = expression(T[t]),
      color = "Signal"
    ) +
    theme_bw()
  
  if (plot_chart) {
    print(p)
  }
  
  result <- list(
    file = file,
    available_types = available_types,
    target_ARL0 = target_ARL0,
    alpha = alpha,
    B = B,
    c_smooth = c_smooth,
    normalized_data = normalized_data,
    event_medians = event_medians_wide_complete,
    global_centers = theta0,
    observed_statistics = chart_data,
    bootstrap_statistics = T_boot,
    UCL_L = UCL_L,
    empirical_p0_from_calibration_bootstrap = empirical_p0,
    empirical_ARL0_from_calibration_bootstrap = empirical_ARL0,
    chart = p
  )
  
  return(result)
}
```

```{r}
res <- stage3A_SBM_L(
  file = file,
  target_ARL0 = 740,
  B = 10000,
  c_smooth = 0.5,
  seed = 123,
  plot_chart = FALSE
)

res$UCL_L
res$observed_statistics
res$chart
```



### C_smooth Function for Justification

```{r}
test_c_for_SBM_L <- function(file,
                             c_grid = c(0, 0.25, 0.5, 1),
                             target_ARL0 = 740,
                             B = 10000,
                             seed = 123) {
  
  purrr::map_dfr(
    c_grid,
    function(c_val) {
      
      res_c <- stage3A_SBM_L(
        file = file,
        target_ARL0 = target_ARL0,
        B = B,
        c_smooth = c_val,
        seed = seed,
        plot_chart = FALSE
      )
      
      data.frame(
        c_smooth = c_val,
        target_ARL0 = res_c$target_ARL0,
        alpha = res_c$alpha,
        B = res_c$B,
        UCL_L = res_c$UCL_L,
        n_signal_observed = sum(res_c$observed_statistics$Signal, na.rm = TRUE),
        max_T_observed = max(res_c$observed_statistics$T_stat, na.rm = TRUE)
      )
    }
  )
}
```

### c_smooth output

```{r}
c_test <- test_c_for_SBM_L(
  file = file,
  c_grid = c(0, 0.25, 0.5, 1),
  target_ARL0 = 740,
  B = 10000,
  seed = 123
)
c_test
```
The UCL was stable for `c_smooth = 0`, `0.25`, and `0.5`, while `c_smooth = 1` produced a larger UCL. Therefore, `c_smooth = 0.5` was selected as the default value because it provides moderate smoothing without excessive UCL inflation.

### Test B Function

```{r}
library(dplyr)
library(purrr)

test_B_for_SBM_L <- function(file,
                             B_max = 30000,
                             B_grid = c(5000, 10000, 20000, 30000),
                             seeds = c(123, 456, 789),
                             target_ARL0 = 740,
                             c_smooth = 0.5) {
  
  alpha <- 1 / target_ARL0
  
  # Basic checks
  if (max(B_grid) > B_max) {
    stop("max(B_grid) must be <= B_max.")
  }
  
  all_results <- purrr::map_dfr(
    seeds,
    function(seed_val) {
      
      message("Running B_max = ", B_max, " with seed = ", seed_val)
      
      time_start <- Sys.time()
      
      res_max <- stage3A_SBM_L(
        file = file,
        target_ARL0 = target_ARL0,
        B = B_max,
        c_smooth = c_smooth,
        seed = seed_val,
        plot_chart = FALSE
      )
      
      time_end <- Sys.time()
      elapsed_sec <- as.numeric(difftime(time_end, time_start, units = "secs"))
      
      T_boot <- res_max$bootstrap_statistics
      T_obs <- res_max$observed_statistics$T_stat
      
      purrr::map_dfr(
        B_grid,
        function(B_val) {
          
          T_sub <- T_boot[seq_len(B_val)]
          
          UCL_val <- as.numeric(
            quantile(
              T_sub,
              probs = 1 - alpha,
              na.rm = TRUE,
              type = 7
            )
          )
          
          p0_hat <- mean(T_sub > UCL_val, na.rm = TRUE)
          ARL0_hat <- ifelse(p0_hat > 0, 1 / p0_hat, Inf)
          
          data.frame(
            seed = seed_val,
            B = B_val,
            c_smooth = c_smooth,
            target_ARL0 = target_ARL0,
            alpha = alpha,
            expected_tail_count = B_val * alpha,
            UCL_L = UCL_val,
            empirical_p0 = p0_hat,
            empirical_ARL0 = ARL0_hat,
            n_signal_observed = sum(T_obs > UCL_val, na.rm = TRUE),
            max_T_observed = max(T_obs, na.rm = TRUE),
            elapsed_sec_for_Bmax_run = elapsed_sec
          )
        }
      )
    }
  )
  
  summary_results <- all_results %>%
    group_by(B) %>%
    summarise(
      c_smooth = first(c_smooth),
      target_ARL0 = first(target_ARL0),
      alpha = first(alpha),
      expected_tail_count = first(expected_tail_count),
      mean_UCL = mean(UCL_L, na.rm = TRUE),
      sd_UCL = sd(UCL_L, na.rm = TRUE),
      min_UCL = min(UCL_L, na.rm = TRUE),
      max_UCL = max(UCL_L, na.rm = TRUE),
      range_UCL = max_UCL - min_UCL,
      mean_empirical_ARL0 = mean(empirical_ARL0, na.rm = TRUE),
      mean_n_signal_observed = mean(n_signal_observed, na.rm = TRUE),
      n_distinct_signal_counts = n_distinct(n_signal_observed),
      .groups = "drop"
    )
  
  # Use largest B in grid as reference
  B_ref <- max(B_grid)
  UCL_ref <- summary_results %>%
    filter(B == B_ref) %>%
    pull(mean_UCL)
  
  summary_results <- summary_results %>%
    mutate(
      abs_diff_from_ref_UCL = abs(mean_UCL - UCL_ref),
      rel_diff_from_ref_pct = 100 * abs(mean_UCL - UCL_ref) / UCL_ref
    )
  
  list(
    raw_results = all_results,
    summary_results = summary_results
  )
}
```

### Test B Output and Conclusion

```{r}

B_test <- test_B_for_SBM_L(
  file = file,
  B_max = 30000,
  B_grid = c(5000, 10000, 20000, 30000),
  seeds = c(123, 456, 789),
  target_ARL0 = 740,
  c_smooth = 0.5
)

B_test$summary_results
```
The UCL and observed monitoring decision were stable across the evaluated bootstrap sizes. Since `B = 10000` produced results close to larger values of `B` while substantially reducing computation time, `B = 10000` was selected for UCL calibration.

## Estimate_ARL1_SBM_L Function

```{r}
estimate_ARL1_SBM_L <- function(res,
                                shift = 1,
                                shifted_types = NULL,
                                shift_mode = c("additive", "multiplicative"),
                                B1 = 5000,
                                seed = 456) {
  
  shift_mode <- match.arg(shift_mode)
  
  library(dplyr)
  
  set.seed(seed)
  
  normalized_data <- res$normalized_data
  available_types <- res$available_types
  theta0 <- res$global_centers
  UCL_L <- res$UCL_L
  c_smooth <- res$c_smooth
  
  if (is.null(shifted_types)) {
    shifted_types <- available_types
  }
  
  shifted_types <- intersect(shifted_types, available_types)
  
  if (length(shifted_types) == 0) {
    stop("No valid shifted_types were provided.")
  }
  
 
  # Create out-of-control shifted data

  
  dat_shift <- normalized_data %>%
    mutate(
      Normalized_shifted = case_when(
        ResidueType %in% shifted_types & shift_mode == "additive" ~
          Normalized + shift,
        
        ResidueType %in% shifted_types & shift_mode == "multiplicative" ~
          Normalized * shift,
        
        TRUE ~ Normalized
      ),
      Normalized_shifted = pmax(0, Normalized_shifted)
    )
  

  # Bootstrap one residue type under shifted condition

  
  bootstrap_one_type_shift <- function(type) {
    
    dat_type <- dat_shift %>%
      filter(ResidueType == type)
    
    locations <- sort(unique(dat_type$Location))
    boot_values <- numeric(length(locations))
    
    for (m in seq_along(locations)) {
      
      loc <- locations[m]
      
      g_loc <- dat_type %>%
        filter(Location == loc) %>%
        pull(Normalized_shifted)
      
      g_loc <- g_loc[!is.na(g_loc)]
      
      if (length(g_loc) == 0) {
        boot_values[m] <- NA_real_
        next
      }
      
      med_g <- median(g_loc)
      mad_g <- median(abs(g_loc - med_g))
      h_loc <- c_smooth * mad_g
      
      sampled_value <- sample(g_loc, size = 1, replace = TRUE)
      eps <- rnorm(1, mean = 0, sd = h_loc)
      
      boot_values[m] <- max(0, sampled_value + eps)
    }
    
    median(boot_values, na.rm = TRUE)
  }
  
 
  # Generate shifted SBM-L statistics

  
  T_shift <- numeric(B1)
  
  for (b in seq_len(B1)) {
    
    boot_medians <- sapply(
      available_types,
      bootstrap_one_type_shift
    )
    
    boot_dplus <- pmax(0, boot_medians - theta0[available_types])
    
    T_shift[b] <- max(boot_dplus, na.rm = TRUE)
  }
  

  # Estimate ARL1 and Monte Carlo precision

  
  signal_indicator <- T_shift > UCL_L
  
  n_signal_shift <- sum(signal_indicator, na.rm = TRUE)
  p1_hat <- mean(signal_indicator, na.rm = TRUE)
  
  ARL1_hat <- ifelse(p1_hat > 0, 1 / p1_hat, Inf)
  
  # Monte Carlo standard error for p1_hat
  se_p1 <- sqrt(p1_hat * (1 - p1_hat) / B1)
  
  # Delta-method standard error for ARL1 = 1 / p1
  se_ARL1 <- ifelse(
    p1_hat > 0,
    se_p1 / (p1_hat^2),
    Inf
  )
  
  relative_se_ARL1 <- ifelse(
    is.finite(ARL1_hat) & ARL1_hat > 0,
    se_ARL1 / ARL1_hat,
    Inf
  )
  
  ARL1_lower <- ifelse(
    is.finite(ARL1_hat),
    max(0, ARL1_hat - 1.96 * se_ARL1),
    Inf
  )
  
  # Sampling distribution is approximately normal
  ARL1_upper <- ifelse(
    is.finite(ARL1_hat),
    ARL1_hat + 1.96 * se_ARL1,
    Inf
  )
  
  data.frame(
    c_smooth = c_smooth,
    target_ARL0 = res$target_ARL0,
    UCL_L = UCL_L,
    shift_mode = shift_mode,
    shift = shift,
    shifted_types = paste(shifted_types, collapse = ", "),
    B1 = B1,
    n_signal_shift = n_signal_shift,
    p1_hat = p1_hat,
    se_p1 = se_p1,
    ARL1_hat = ARL1_hat,
    se_ARL1 = se_ARL1,
    relative_se_ARL1 = relative_se_ARL1,
    ARL1_lower = ARL1_lower,
    ARL1_upper = ARL1_upper
  )
}
```
In this analysis, only additive shifts are used. The multiplicative option is retained in the function for flexibility but is not used in the reported ARL1 evaluation. On the USL-normalized scale, an additive shift of 1 corresponds to an increase of 1% of USL.

## Test_B1_for_ARL1 Function

```{r}
test_B1_for_ARL1 <- function(res,
                             B1_grid = c(1000, 3000, 5000, 10000, 20000),
                             seeds = c(123, 456, 789),
                             shift = 1,
                             shifted_types = c("DAR", "CAR", "Mic"),
                             shift_mode = "additive") {
  
  library(dplyr)
  library(purrr)
  
  all_results <- purrr::map_dfr(
    seeds,
    function(seed_val) {
      
      purrr::map_dfr(
        B1_grid,
        function(B1_val) {
          
          message(
            "Running ARL1 with B1 = ", B1_val,
            ", seed = ", seed_val
          )
          
          time_start <- Sys.time()
          
          out <- estimate_ARL1_SBM_L(
            res = res,
            shift = shift,
            shifted_types = shifted_types,
            shift_mode = shift_mode,
            B1 = B1_val,
            seed = seed_val
          )
          
          time_end <- Sys.time()
          
          out$seed <- seed_val
          out$elapsed_sec <- as.numeric(
            difftime(time_end, time_start, units = "secs")
          )
          
          out
        }
      )
    }
  )
  
  summary_results <- all_results %>%
    group_by(B1) %>%
    summarise(
      shift = first(shift),
      shifted_types = first(shifted_types),
      shift_mode = first(shift_mode),
      mean_n_signal_shift = mean(n_signal_shift, na.rm = TRUE),
      min_n_signal_shift = min(n_signal_shift, na.rm = TRUE),
      max_n_signal_shift = max(n_signal_shift, na.rm = TRUE),
      mean_p1_hat = mean(p1_hat, na.rm = TRUE),
      sd_p1_hat = sd(p1_hat, na.rm = TRUE),
      mean_ARL1 = mean(ARL1_hat, na.rm = TRUE),
      sd_ARL1 = sd(ARL1_hat, na.rm = TRUE),
      mean_se_ARL1 = mean(se_ARL1, na.rm = TRUE),
      mean_relative_se_ARL1 = mean(relative_se_ARL1, na.rm = TRUE),
      mean_ARL1_lower = mean(ARL1_lower, na.rm = TRUE),
      mean_ARL1_upper = mean(ARL1_upper, na.rm = TRUE),
      mean_elapsed_sec = mean(elapsed_sec, na.rm = TRUE),
      .groups = "drop"
    )
  
  # Use largest B1 as reference
  B1_ref <- max(B1_grid)
  
  ARL1_ref <- summary_results %>%
    filter(B1 == B1_ref) %>%
    pull(mean_ARL1)
  
  summary_results <- summary_results %>%
    mutate(
      abs_diff_from_ref_ARL1 = abs(mean_ARL1 - ARL1_ref),
      rel_diff_from_ref_ARL1_pct =
        100 * abs(mean_ARL1 - ARL1_ref) / ARL1_ref
    )
  
  list(
    raw_results = all_results,
    summary_results = summary_results
  )
}
```

### B1 Test Output and Conclusion

```{r}
B1_test <- test_B1_for_ARL1(
  res = res,
  B1_grid = c(1000, 3000, 5000, 10000, 20000),
  seeds = c(123, 456, 789),
  shift = 1,
  shifted_types = c("DAR", "CAR", "Mic"),
  shift_mode = "additive"
)
print(B1_test$summary_results, width = Inf)
#B1_test$summary_results
```

```{r final-arl1-shift-1}
arl1_shift_1 <- estimate_ARL1_SBM_L(
  res = res,
  shift = 1,
  shifted_types = c("DAR", "CAR", "Mic"),
  shift_mode = "additive",
  B1 = 5000,
  seed = 456
)

arl1_shift_1
```

For a global additive shift of +1% USL across DAR, CAR, and Mic, the estimated ARL1 was obtained using `B1 = 5000`. Although this shift is small relative to the USL, it may represent a meaningful increase relative to the observed baseline residue levels.

```{r final-arl1-grid}
shift_grid <- c(0.25, 0.5, 1, 2, 3, 5)

arl1_grid <- purrr::map_dfr(
  shift_grid,
  function(delta) {
    estimate_ARL1_SBM_L(
      res = res,
      shift = delta,
      shifted_types = c("DAR", "CAR", "Mic"),
      shift_mode = "additive",
      B1 = 5000,
      seed = 456
    )
  }
)

arl1_grid
```


The ARL1 estimates stabilized for `B1 >= 5000`. At `B1 = 5000`, the average number of shifted signals was adequate and the relative Monte Carlo standard error was below 10%. Therefore, `B1 = 5000` was selected for ARL1 estimation to balance precision and computational efficiency.